SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-20 scipy-1.0/paper.tex
Add some links
Refine conference section

@@

@@

% stefan, gael, david, jarrod,

@@

scikit-learn
\subsection*{Release History}

@@

>>>>

http://conference.scipy.org/proceedings/scipy2008/paper\_0/full\_text.pdf
http://conference.scipy.org/proceedings/scipy2008/paper\_1/full\_text.pdf

The first SciPy workshop was held in September 2002 at CalTech—a
single track, two day event with 50 participants, many of them
developers of SciPy and surrounding libraries.  In the early
workshops, recurrent topics indicate the state of development, with
emphasis being placed on the underlying array package, plotting,
parallel processing, acceleration / wrapping, and user interfaces.  By
2004, a significant shift occurred towards application of SciPy on
scientific problems.  The event also started to draw in more keynote
speakers from outside the community, such as Guido van Rossum (creator
of Python, 2006), Ivan Krstić (One Laptop per Child, 2007), Alex
Martelli (Google, 2008), and Peter Norvig (Google Research, 2009).

%2002—https://web.archive.org/web/20021020215937/http://www.scipy.org:80/site_content/scipy02/scipy02_agenda.htm
%2003—https://web.archive.org/web/20031207151811/http://www.scipy.org:80/site_content/scipy03/
%2004—Jim Hugunin
https://web.archive.org/web/20040920080225/http://www.scipy.org:80/wikis/scipy04
%Travis Oliphant 2005—https://web.archive.org/web/20051103155042/http://www.scipy.org:80/wikis/scipy05/FrontPage
%Guido—2006 https://scipy.github.io/old-wiki/pages/SciPy2006.html
%Martelli—2008 https://scipy.github.io/old-wiki/pages/Developer_Zone/Conferences/SciPy2004.html
%Norvig—2009 https://scipy.github.io/old-wiki/pages/Developer_Zone/Conferences/SciPy2005.html

While the US SciPy conference kept growing (by ... it had multiple
tracks, student sponsorship, proceedings, and funding), satellite
events were being organized by volunteers elsewhere, such as EuroSciPy
(2008–) and SciPy India (2009–).

@@

FOSSEE

@@

% stefan, gael, david, jarrod, robert

@@

scikit-learn

% scikits
%https://mail.python.org/pipermail/scipy-dev/2006-November/006315.html
%https://mail.python.org/pipermail/scipy-dev/2006-November/006316.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006972.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006835.html

% roadmap
%https://mail.python.org/pipermail/scipy-dev/2007-March/006808.html

% scikit learn
%https://mail.python.org/pipermail/scipy-dev/2007-July/007451.html

\subsection*{Release History}

@@

% Release management

% Jarrod
%https://mail.python.org/pipermail/scipy-dev/2007-August/007613.html
%Ralf
%https://mail.python.org/pipermail/numpy-discussion/2010-March/049057.html
%https://mail.python.org/pipermail/scipy-dev/2010-March/014034.html
%https://mail.python.org/pipermail/scipy-dev/2010-April/014091.html
